Doppler Imaging Fun

### 2019-07-02 tex/gitlinks.tex
better notation

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
